Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2023-04-17 paper/ms.tex
Remove HST and add new fig1

\section{Introduction}
\label{sec:intro}
\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{fig/mockHST.pdf}
    \caption{Synthetic Hubble Space Telescope images of our simulations with and
    without the interstellar medium. The upper panels show an \Nbody{} only
    simulation while the lower panels show a simulation which includes the
    \SMUGGLE{} model for the interstellar medium. Each panel is
    $20\,\textrm{kpc}$ to a side. Columns show different points in time,
    separated by $1\,\textrm{Gyr}$. We can see that in the \Nbody{} run, the bar
    grows in length and strength. In the \SMUGGLE{} run, the bar remains at
    approximately the same length and strength over the course of the
    simulation. The \Nbody{} model is identical to the GALAKOS model {\bf (with
    different particle numbers and softening lengths)}, discussed in the text.
    Details on the production of these synthetic images is given in
    Appendix~\ref{app:hst}.}\label{fig:overview}
\end{figure*}

@@

We show synthetic \textit{Hubble Space Telescope} images of our barred galaxy in
a case with and without gas in Fig.~\ref{fig:overview}. We see that the bar
grows longer and stronger without gas, while it remains at approximately the
same length and strength when gas is included. Details on the production of
these synthetic images are given in Appendix~\ref{app:hst}.

@@

\section{Idealized Mock Light Images}
\label{app:hst}
We created synthetic mock light images at $1024^2$ resolution in
Fig.~\ref{fig:overview} for the \textit{Hubble Space Telescope} using a
post-processed Monte Carlo radiation transfer simulation with the SKIRT9 code
including secondary emission from dust \citep{2020AC....3100381C}. Emission from
star particles was calculated assuming a Bruzual-Charlot spectral energy
distribution \citep{2003MNRAS.344.1000B} and a Chabrier initial stellar mass
function \citep{2003PASP..115..763C}. The luminosity from each star particle was
smoothed using a cubic spline kernel with each star particle being assigned a
smoothing length equal to its distance to its $32$nd closest neighbor. We
launched $10^9$ photon packets per simulation segment. For star particles
which were present in the initial simulation (i.e., initial disk and bulge
particles), we assumed that they have an age of $5\,\textrm{Gyr}$ and solar
metallicity. For star particles in the \SMUGGLE{} simulation which are newly
formed, we used their recorded ages and metallicities.

For the \SMUGGLE{} simulations, we included absorption and emission from dust. We
assumed the THEMIS (The Heterogeneous dust Evolution Model for Interstellar
Solids) dust model \citep{2017AA...602A..46J} to convert gas metallicity and
mass density to dust mass density. For the \Nbody{} simulations we ran the
SKIRT9 code in a mode without an obscuring medium, but otherwise applied the
same procedure.

We used the profiles for filters F814W, F606W, and F475W on the Advanced
Camera for Surveys (ACS) instrument for red, green, and blue pixel values,
respectively. Filtered fluxes were converted to RGB values using an $\arcsinh$
scaling following \citet{2004PASP..116..133L} Scalings and cutoff values
were adjusted manually to create visually appealing images. Filter profiles
were provided by the Spanish Virtual Observatory Filter
Service \citep{2012ivoa.rept.1015R, 2020sea..confE.182R}.

>>>>

\section{Introduction}
\label{sec:intro}
\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{fig/fig1.pdf}
    \caption{{\bf Stellar mass distribution of our simulations with and without
    the interstellar medium.} The upper panels show an \Nbody{} only simulation
    while the lower panels show a simulation which includes the \SMUGGLE{} model
    for the interstellar medium. Each panel is $20\,\textrm{kpc}$ to a side.
    {\bf The bar length is shown as a solid white bar (details on its
    computation are given in the text). The corotation radius is shown as a
    dashed white circle.} Columns show different points in time, separated by
    $1\,\textrm{Gyr}$. We can see that in the \Nbody{} run, the bar grows in
    length and strength. In the \SMUGGLE{} run, the bar remains at approximately
    the same length and strength over the course of the simulation. The \Nbody{}
    model is identical to the GALAKOS model {\bf (with different particle
    numbers and softening lengths)}, discussed in the text.}\label{fig:overview}
\end{figure*}

@@

We show {\bf stellar mass distributions} of our barred galaxy in a case with and
without gas in Fig.~\ref{fig:overview}. We see that the bar grows longer and
stronger without gas ({\bf bar length shown as a white bar}), while it remains
at approximately the same length and strength when gas is included. {\bf As the
bar without gas slows down, the corotation radius (white dashed circle) grows
larger with time.}

@@
